Reanalysis Step 5: Main Effects Outcome Analysis

### 2025-08-31 reanalysis-5-outcome_analysis.qmd
fix coefficient

# Extract main effect of lapse
lapse_effect <- pooled_results[pooled_results$term == "ever_lapse_binary", ]

@@

# Get the lapse coefficient from each model
for (i in 1:n_imputations) {
  # Extract from model summaries
  lapse_row <- model_summaries[[i]][model_summaries[[i]]$term == "ever_lapse_binary", ]

@@

# Display key variables
key_vars <- c("ever_lapse_binary")
key_results <- full_results[full_results$Variable %in% key_vars, ]

@@

    # Calculate AME with clustering and weights
    # marginaleffects handles survey designs well
    ame <- avg_slopes(
      fitted_models[[i]], 
      variables = "ever_lapse_binary",
      newdata = imp_data,
      vcov = ~e_mrn_deidentified,  # Cluster SEs on patient ID
      wts = imp_data$weights  # Apply PS weights
    )

>>>>

# Extract main effect of lapse
lapse_effect <- pooled_results[pooled_results$term == "ever_lapse_binary1", ]

@@

# Get the lapse coefficient from each model
for (i in 1:n_imputations) {
  # Extract from model summaries
  lapse_row <- model_summaries[[i]][model_summaries[[i]]$term == "ever_lapse_binary1", ]

@@

# Display key variables
key_vars <- c("ever_lapse_binary1")
key_results <- full_results[full_results$Variable %in% key_vars, ]

@@

    # Calculate AME with clustering and weights
    # marginaleffects handles survey designs well
    ame <- avg_slopes(
      fitted_models[[i]], 
      variables = "ever_lapse_binary1",
      newdata = imp_data,
      vcov = ~e_mrn_deidentified,  # Cluster SEs on patient ID
      wts = imp_data$weights  # Apply PS weights
    )
